Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-23 code/analysis.Rmd
fixed tke plot

TKEplot <- final %>%
  filter(eta>0) %>%
  arrange(frontal_area, u) %>%
  select(dowel_density, u, eta, deta) %>%
  mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  labs(y = "Effective Capture Efficiency", x = "Turbulent Kinetic Energy")

>>>>

TKEplot <- final %>%
  filter(eta>0) %>%
  arrange(frontal_area, u) %>%
  select(dowel_density, u, eta, deta) %>%
  mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulent Kinetic Energy (",mm^{2}/s^{2},")")))
